Numerical Stability of Detonations in White Dwarf Simulations

### 2018-11-22 papers/ignition/paper.tex
Mention the network used
Add self-heating figure

Our test problem is inspired by \cite{kushnir:2013}, and very loosely approximates the
conditions of two $0.64\ \msolar$ WDs colliding head-on. The simulation domain is 1D with a
reflecting boundary at $x = 0$. For $x > 0$ there is a uniform fluid composed (by mass)
of $50\%\, ^{12}$C, $45\%\, ^{16}$O, and $5\%\, ^{4}$He. The fluid is relatively cold,
$T = 10^7$ K, has density $\rho = 5 \times 10^6$ g/cm$^3$, and is traveling toward the
origin with velocity $-2 \times 10^8$ m/s. A uniform constant gravitational acceleration
is applied, $g = -1.1 \times 10^8$ m/s$^{2}$. This setup causes a sharp initial release
of energy at $x = 0$, and the primary question is whether a detonation occurs promptly
near this contact point, or occurs later (possibly at a distance from the contact point).
The simulated domain has width $1.6384 \times 10^9$ cm, and we apply inflow boundary conditions
that keep feeding the domain with material that has the same conditions as the initial fluid.
Simulations are performed with the adaptive mesh refinement (AMR) code \castro\
\citep{castro, astronum:2017}.

@@

>>>>

Our test problem is inspired by \cite{kushnir:2013}, and very loosely approximates the
conditions of two $0.64\ \msolar$ WDs colliding head-on. The simulation domain is 1D with a
reflecting boundary at $x = 0$. For $x > 0$ there is a uniform fluid composed (by mass)
of $50\%\, ^{12}$C, $45\%\, ^{16}$O, and $5\%\, ^{4}$He. The fluid is relatively cold,
$T = 10^7$ K, has density $\rho = 5 \times 10^6$ g/cm$^3$, and is traveling toward the
origin with velocity $-2 \times 10^8$ m/s. A uniform constant gravitational acceleration
is applied, $g = -1.1 \times 10^8$ m/s$^{2}$. This setup causes a sharp initial release
of energy at $x = 0$, and the primary question is whether a detonation occurs promptly
near this contact point, or occurs later (possibly at a distance from the contact point).
The simulated domain has width $1.6384 \times 10^9$ cm, and we apply inflow boundary conditions
that keep feeding the domain with material that has the same conditions as the initial fluid.
Simulations are performed with the adaptive mesh refinement (AMR) code \castro\
\citep{castro, astronum:2017}. For the burning we use the alpha-chain nuclear network
\texttt{aprox13}. The results we describe below do not strongly depend on the network.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.525]{{{plots/amr_ignition_self-heat}}}
  \caption{Distance from the contact point of the ignition as a function of finest
           spatial resolution. The solid black curve with circle markers represents
           the simulations with uniform resolution (no AMR). The other curves represent
           simulations with a fixed base resolution and varying amounts of AMR.
           \label{fig:self-heat-distance}}
\end{figure}

\autoref{fig:self-heat-distance} shows our main results.
